\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{geometry}
\geometry{margin=1in}
\setstretch{1.25}

\title{Snapshot Objectives}
\author{Group 6}
\date{}

\begin{document}

\maketitle

\section*{Start Objective}

The start of the project focuses on establishing the foundation necessary for building the YouTube Comment Comparison Web Application. The main goal of this phase is to clearly define the project's vision and prepare the technical base for development.

\subsection*{Goals}
\begin{itemize}
    \item Define the core purpose and intended functionality of the application.
    \item Conduct brainstorming sessions to refine features and workflow.
    \item Determine team roles and responsibilities.
    \item Establish a version control and collaboration workflow.
\end{itemize}

\subsection*{Technical Setup}
\begin{itemize}
    \item Initialize the React frontend and Node.js/Fastify backend.
    \item Configure dependencies such as Axios and environment variables.
    \item Develop basic frontend pages (homepage and results template).
    \item Create the initial database schema and connect it to backend services.
    \item Set up and test basic API routes to verify frontend–backend communication.
\end{itemize}

\section*{1st Checkpoint Objective}
This checkpoint reflects on the progress made during the startup phase and shifts focus toward integrating the YouTube API and preparing the system for deployment.

\subsection*{Completed From Previous Stage}
\begin{itemize}
    \item Core architecture established (frontend, backend, database).
    \item Foundational pages and backend routes created.
    \item Verified communication across all major components.
\end{itemize}

\subsection*{New Tasks Added}
\begin{itemize}
    \item Implement YouTube URL validation on the frontend.
    \item Authenticate and connect to the YouTube Data API.
    \item Fetch video details, comments, and commenter IDs.
    \item Store video data and commenter IDs in the database.
\end{itemize}

\subsection*{Deployment Work}
\begin{itemize}
    \item Deploy the frontend to Vercel.
    \item Deploy the backend and database to Railway or Supabase.
    \item Perform end-to-end testing across all deployed services.
\end{itemize}

\section*{2nd Checkpoint Objective}
With API integration complete, this checkpoint emphasizes data analysis features and user-facing visualizations.

\subsection*{Reflection on Previous Work}
\begin{itemize}
    \item The system can now fetch and store YouTube video and commenter data.
    \item Deployment pipeline is set up and functional.
\end{itemize}

\subsection*{New Tasks Added}
\begin{itemize}
    \item Implement algorithms to compare commenter data across videos.
    \item Compute shared commenter statistics and percentages.
    \item Generate per-video insights based on comparison results.
    \item Create visual components such as:
          \begin{itemize}
              \item Charts (bar, donut, line, etc.)
              \item Tables for numerical breakdowns
          \end{itemize}
    \item Add filtering and sorting options for user navigation.
\end{itemize}

\section*{Due Date Checkpoint Objective}
The final checkpoint focuses on finalizing the application, improving the user interface, and outlining long-term enhancements.

\subsection*{Reflection on Completed Work}
\begin{itemize}
    \item Comparison algorithms implemented and validated.
    \item Visualization features added to the frontend.
    \item Deployment is stable and functioning end-to-end.
\end{itemize}

\subsection*{Finishing Tasks}
\begin{itemize}
    \item Improve UI/UX design for clarity and aesthetics.
    \item Ensure responsiveness and accessibility across devices.
\end{itemize}

\subsection*{Future Work (Post-MVP)}
\begin{itemize}
    \item Add a user login/authentication system.
    \item Implement saving/viewing of comparison history.
    \item Explore advanced analytics (e.g., sentiment analysis, demographic insights).
\end{itemize}

\end{document}
