\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}
\setlength{\parindent}{2em}


\title{\textbf{User Manual}}
\author{Group 6: Momoka, Kade, Alexander, Tae Ha}
\date{}
\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Important Message for Professor}
Please use commit history to check our updates instead of the Snapshot Tags. We weren't very knowledgeable on how tagging worked and didn't realize it only points to a specific commit without the ability to push future commits to organize commits from different times and different members into individual Snapshots.

\section{Jira Link}
Get jira link from Xander and input here

\section{Objective Breakdown}
This Audience Analytics webapp is to compare the user's channel against another user-chosen channel. It will then go through a number of videos specified by the user and provide stats regarding the shared audience between the two channels.

\section{Significance and Goals}
 The goal of this webapp is to provide newer content creators with a tool that can help them analyze their audience and provide insights on what kind of content their audience is interested in.
 
 While the information provided may seem limited at first glance, the primary intention of the app is provide helpful information that the user can consider regarding their channel's content and growth without strictly suggesting any action they should take.

\section{How to Use}
\begin{enumerate}
\item Enter the webapp URL into the browser
\item Enter your own Youtube channel URL into 'My Channel'
\item Enter URL of the Youtube channel you want to compare against in 'Compare to: '
\item Specify number of videos you want to compare (1~20)
\item Select whether to compare videos from 'Most Recent' or 'Most Viewed'
\item The webapp will display stats on the total number of shared commenters and per-video w/ the option to sort based on shared commenter count, viewer count, or recency
\end{enumerate}
\newpage

\section{Changelog}
\begin{enumerate}
\item ver. 1: base user manual w/ objective breakdown, significance, and how to use.
\item ver. 2: included description of sorting options
\end{enumerate}
\end{document}
